---
title: "BSMM-lab-2"
subtitle: "BSMM 8740 Fall 2023"
author: "Vijaya Satwika Naidu Mandali"
date: "25-September-2023"
format: html
editor: visual
self-contained: true
---

## Setup

```{r}
install.packages("tidymodels")
install.packages("gt")
install.packages("gtExtras")
install.packages("DataExplorer")
```

```{r}
library(magrittr)     # the pipe
library(tidyverse)    # for data wrangling + visualization
library(tidymodels)   # for modeling
library(gt)           # for making display tables
library(gtExtras)     # helper functions for beautiful tables
library(DataExplorer) #
```

Load packages and data:

```{r load-pkg-data}
#| message: false
the_tate <- readr::read_delim("data/the-tate-collection.csv", ";", escape_double = FALSE, trim_ws = TRUE)
the_tate_artists <- readr::read_csv("data/the-tate-artists.csv")
```

## Exercises

### Exercise 1

```{r}
#dplyr::summarize(the_tate)
dplyr::glimpse(the_tate)
```

```{r}
dplyr::glimpse(the_tate_artists)
```

```{r}
#uniqueartists <- the_tate_artists |>
artists<- the_tate |>
  dplyr::select(artist)  
dplyr::distinct(artists)
```

```{r}
max(the_tate_artists$yearOfBirth, na.rm = T)
```

The `the_tate` dataset has \_\_\_ unique artists who worked from \_\_\_ to \_\_\_. The works were acquired between the years \_\_\_ and \_\_\_.

### Exercise 2

How number of works with missing dates is \_\_.

The number of artists whose works have missing dates is \_\_.

It would require resolving missing year data for only \_\_ artists resolve resolve at least 50% of the missing data.

The missing year data likely to be classified as \_\_\_\_.

### Exercise 3

The artist with the most works in the Tate collection is \_\_\_.

The artist with the tenth-most works in the Tate collection is \_\_\_.

### Exercise 4

The artist with the greatest number of works in the Tate collection represent \_\_\_% of the total number of works

### Exercise 5

There are \_\_ duplicate artist-title pairs

### Exercise 6

The artist with the largest work in the tate collection is \_\_\_

The artist with the smallest work in the collection is \_\_\_. The smallest work has area \_\_\_ $\text{cm}^2$

### Exercise 7

...

### Exercise 8

The annual return in the SPX price in 2020 was \_\_\_%.

The corresponding price volatility was \_\_\_%.

### Exercise 9

The period volatility was \_\_\_.\_%

### 
